Developing an AI-Assisted Grading System Using Large Language Models (GPT-4)

### 2024-12-10 src/paper.tex
final touches to testing section by Dr. A.

While a full testing methodology is not required at this stage, we plan to conduct targeted testing activities to ensure that the system meets its key objectives. The testing will focus on verifying functionality, accuracy, and usability.

@@

\begin{itemize}
    \item \textbf{Basic Functional Tests:}  
    Verify that the backend API correctly processes images and text submissions, interacts with GPT-4 Vision, and returns the expected output. Confirm that the frontend can display graded results, allow for rubric application, and handle user authentication.

@@

    \item \textbf{Semantic Grouping Verification:}  
    Input multiple variations of a correct response and a few incorrect ones. Check that the AI groups similar answers together and isolates outliers. Teachers reviewing these groups should find the clustering logical and helpful for grading.

    \item \textbf{Rubric and Grading Validation:}  
    Apply rubrics to test questions and confirm that the final scores are computed as expected. Check that changing a rubric value updates all affected scores consistently.

    \item \textbf{User Interface and Workflow Checks:}  
    Have a small set of instructors perform typical grading tasks. Gather feedback on the interface clarity, ease of navigation, and overall efficiency. Any confusing elements or inefficiencies will be noted for improvement.

@@

These initial tests will inform further refinements and pave the way for more comprehensive evaluations in a future development phase.

>>>>

We plan to conduct targeted testing activities to ensure that the system meets its key objectives. The testing will focus on verifying \emph{functionality}, \emph{accuracy}, and \emph{usability}.

@@

\begin{itemize}
    \item \textbf{Basic Functional Tests:}  
    Verify that the backend API correctly processes submissions, interacts with GPT-4 Vision, and returns the expected output. Confirm that the frontend can display graded results, and rubric application.

@@

    \item \textbf{Semantic Grouping, Accuracy Verification:}  
    Input multiple variations of a correct response and a few incorrect ones. Check that the AI groups similar answers together and isolates outliers. Teachers reviewing these groups should find the clustering logical and helpful for grading.

    \item \textbf{Rubric and Grading Accuracy Tests:}  
    Apply rubrics to test questions and confirm that the final scores are computed as expected. Check that changing a rubric value updates all affected scores consistently.

    \item \textbf{User Interface and Workflow Usability Checks:}  
    Have a small set of instructors perform typical grading tasks. Gather feedback on the interface clarity, ease of navigation, and overall efficiency. Any confusing elements or inefficiencies will be noted for improvement.

@@

These tests will inform further refinements and pave the way for more comprehensive evaluations in a future development phase.
